Seasonal Variations in Marriage License Applications

### 2024-09-27 paper/paper.qmd
llm usage edit

Wile there have been studies showing decreases in marriage licences during global crisis, there has been little analysis on how local trends are influenced by emotionally significant dates or practicality. This paper fills that gap by examining the effect of these periods on marriage decisions in Toronto, providing information on how tradition, emotion, and practicality play a part in these decisions.

@@

## Licenses by Year and Month
```{r}
#| label: fig-licenses-heatmap
#| fig-cap: "Heatmap of Marriage Licenses by Year and Month"
#| echo: false
#| warning: false
#| message: false

@@

One of the clearest patters shown from the data is the overwhelming preference for summer months when it comes t getting married. Across all years, these moths far exceed other months. This is largely attributed to the fact that during summer, logistics are much easier to work out. People are able to have weddings outside which is usually preferred. People also do not have to worry about bad weather like snow storms or heavy wind. Having a wedding during the summer also makes pictures look better since the sun is shining pretty well. In terms of guest availability, summer is usually optimal because there is no school, and many people take time off work. 
Even thought dates like valentines day hold cultural and romantic significance, they do not show a corresponding increase in marriage activity. This indicates that while couples may enjoy celebrating love or symbolic days, their wedding planning is more practically driven by factors like convenience, weather, and timing.

>>>>

While there have been studies such as [@citeforbes2021] which show decreases in marriage licences during global crisis like COVID-19, there has been little analysis on how local trends are influenced by emotionally significant dates or practicality. This paper fills that gap by examining the effect of these periods on marriage decisions in Toronto, providing information on how tradition, emotion, and practicality play a part in these decisions.

@@

## Licenses by Year and Month
```{r}
#| label: fig-licenses-heatmap
#| fig-cap: "Heatmap of Marriage Licenses by Year and Month"
#| echo: false
#| warning: false
#| message: false
#https://www.datanovia.com/en/lessons/heatmap-in-r-static-and-interactive-visualization/#:~:text=A%20basic%20heatmap%20can%20be,parameters%20such%20as%20cell%20size. was referenced to make heatmap.

@@

One of the clearest patters shown from the data is the overwhelming preference for summer months when it comes t getting married. Across all years, these moths far exceed other months. This is largely attributed to the fact that during summer, logistics are much easier to work out. People are able to have weddings outside which is usually preferred. People also do not have to worry about bad weather like snow storms or heavy wind. Having a wedding during the summer also makes pictures look better since the sun is shining pretty well. In terms of guest availability, summer is usually optimal because there is no school, and many people take time off work.

Even thought dates like valentines day hold cultural and romantic significance, they do not show a corresponding increase in marriage activity. This indicates that while couples may enjoy celebrating love or symbolic days, their wedding planning is more practically driven by factors like convenience, weather, and timing.
